Analysis

### 2022-04-07 analysis/analysis.Rmd
updated materialized analysis rmd

mapview(pollen_locations.sf)

@@

```{r}
mapview(st_as_sf(c14,
                 coords = c("lng", "lat"), 
                 crs = 4326),layer.name = "14C Data"
        )
```

@@

```{r}
c14.calibrated <- calibrate(x = c14$bp, errors = c14$std)
```

@@

```{r}
sumcal <- spd(c14.calibrated, timeRange = 1950-timeframe, bins = c14$site, runm = sw)
```

@@

```{r}
mapview(st_as_sf(sites,
                 coords = c("LV03_Rechtswert_fuzzy", "LV03_Hochwert_fuzzy"),
                 crs = 21781),
        layer.name = "Sites"
)
```

@@

```{r}
res.lss[res.lss$date %in%
seq(from=timeframe[1],
    to=timeframe[2], by=50),]
res.lss$age <- 1950-res.lss$date
```

@@

@@

```{r}
start_time <- Sys.time()
while (!enough_samples) {

@@

>>>>

pollenmap <- tempfile(fileext = ".png")
mapshot(
  mapview(pollen_locations.sf),
  file = pollenmap
  )
knitr::include_graphics(pollenmap)

@@

```{r}
c14map <- tempfile(fileext = ".png")
mapshot(
  mapview(st_as_sf(c14,
                   coords = c("lng", "lat"), 
                   crs = 4326),layer.name = "14C Data"
          ),
  file = c14map
  )
knitr::include_graphics(c14map)
```

@@

```{r}
c14.calibrated <- calibrate(x = c14$bp, errors = c14$std, verbose = F)
```

@@

```{r}
sumcal <- spd(c14.calibrated, timeRange = 1950-timeframe, bins = c14$site, runm = sw, verbose = F)
```

@@

```{r}
sitesmap <- tempfile(fileext = ".png")
mapshot(
  mapview(st_as_sf(sites,
                   coords = c("LV03_Rechtswert_fuzzy", "LV03_Hochwert_fuzzy"),
                   crs = 21781),
          layer.name = "Sites"
  ),
  file = sitesmap
)
knitr::include_graphics(sitesmap)
```

@@

```{r}
res.lss <- res.lss[res.lss$date %in% seq(from=timeframe[1],
                                         to=timeframe[2], by=50),
        ]
res.lss$age <- 1950-res.lss$date
```

@@

The final run after convergence to get more than the min 10000 effective samples for each parameter takes quite some time. On my machine, it took nearly 5 hours. Therefore, I add a switch here for not doing this analysis, but feel free to proceed yourself, if you like:

```{r}
do_final_run = F
```

@@

```{r}
start_time <- Sys.time()
while (!enough_samples & do_final_run) {

@@

If the final run above was skipped, but you have already the results from a previous run, you can load this at this stage:

```{r}
collector <- readRDS("mcmc_collector.RDS")
```
